Allocation Removal by Partial Evaluation in a Tracing JIT

### 2010-10-06 talk/pepm2011/paper.tex
shuffle stuff around
mention similarity to execution semantics

XXX is "symbolic execution" the right word to drop?

@@

When the optimizer sees a new operation, it optimistically removes it and
assumes that the resulting object can stay static. The optimization for all
further operations is split into two cases. One case is for when the
involved variables are in the static heap, which means that the operation can be
removed. The other case is that nothing is known about the variables, which
means the operation has to be residualized.

@@

>>>>

XXX rewrite to acknowledge the existence of the formal stuff

@@

When the optimizer sees a new operation, it optimistically removes it and
assumes that the resulting object can stay static. The optimization for all
further operations is split into two cases. One case is for when the
involved variables are in the static heap, which means that the operation can be
performed at optimization time and removed from the trace. These rules mirror
the execution semantics closely. The other case is that nothing is known about
the variables, which means the operation has to be residualized.

@@

\subsection{Analysis of the Algorithm}
\label{sub:analysis}

XXX algorithm is linear in the length of the trace

% subsection Analysis of the Algorithm (end)
